---
title: "Untitled"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    source_code : "https://github.com"
    storyboard: true
    theme: lumen
---

Monthly deaths from bronchitis, emphysema and asthma in the
UK, 1974–1979 (Source: P. J. Diggle, 1990, Time Series: A
Biostatistical Introduction. Oxford, table A.3)

```{r setup, include=FALSE}
library(flexdashboard)
library(DT)
```

Page 1
======================================================================

Column {data-width=650}
-----------------------------------------------------------------------

### Chart A {data-padding = 20}

```{r, shiny}
DT::datatable(mtcars,options = list(bPaginate = FALSE))
```

Column {data-width=350}
-----------------------------------------------------------------------

### Chart B

```{r}

```

### Chart C

```{r}

```

Page 2
=========================================================================

### About dygraphs
This example makes use of the dygraphs R package. The dygraphs
package provides rich facilities for charting time-series data
in R. You can use dygraphs at the R console, within R Markdown
documents, and within Shiny applications.